Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-30 scagnostics.Rmd
Updated pipe trace plots according to issues.

\textcolor{red}{Sometimes index value decreases, because index is not rotationally invariant.}

@@

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
if(!file.exists("cache/pipeFirstRun.rda")){
  pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
  pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
  save(pipeTourRes, pipeTourResMelt, file = "cache/pipeFirstRun.rda")
} else {
  load("cache/pipeFirstRun.rda")
}
newBasisPipeTour <- which(attributes(interpolate(pipeTour))$new_basis)
ggplot(pipeTourResMelt, aes(x=t, y=value)) +
  geom_line() + 
  facet_wrap(~variable, ncol=1, scales = "free_y")+
  geom_vline(data=as.tibble(newBasisPipeTour), mapping=aes(xintercept=value), color="red")
```

>>>>

\textcolor{red}{Sometimes index value decreases, because index is not rotationally invariant.}
\textcolor{red}{Updated the plot, makes it look like skinny, 1-convex should be better index to optimise, however in practice this is not the case, probably because TIC is less sensitive to fluctuations, making it more robust against getting stuck in local maxima.}

@@

```{r pipeFirstRun,fig.width=6, fig.height=7, fig.cap="Index value on tour path when scouting for high TIC index values."}
if(!file.exists("cache/pipeFirstRun.rda")){
  pipeTourRes <- getProj(pipe1000, pipeTourFull, "Pipe", 1000)
  pipeTourResMelt <- melt(pipeTourRes, id=c("t", "name", "size"))
  save(pipeTourRes, pipeTourResMelt, file = "cache/pipeFirstRun.rda")
} else {
  load("cache/pipeFirstRun.rda")
}
newBasisPipeTour <- pipeTourResMelt %>%
  filter(t %in% which(attributes(interpolate(pipeTour))$new_basis))
ggplot(newBasisPipeTour, aes(x=t, y=value)) +
  geom_point(mapping=aes(color=(variable=="TIC"))) + 
  scale_colour_manual(values = c("black", "red")) +
  facet_wrap(~variable, ncol=1) +
  guides(color=FALSE) +
  ylim(c(0,1))
```
